% YAAC Another Awesome CV LaTeX Template
%
% This template has been downloaded from:
% https://github.com/darwiin/yaac-another-awesome-cv
%
% Author:
% Christophe Roger
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%Section: Work Experience at the top
\sectionTitle{Professional Experience}{\faSuitcase}
%\renewcommand{\labelitemi}{$\bullet$}
\begin{experiences}
  \experience
    {January 2019} {AI Developer | BYON8}{Stockholm}{Sweden}
    {Now}    {\begin{itemize}
               \item Byon8 is a health tech company using artificial intelligence in medical diagnostics. With our product AITOPYA, healthcare professionals are provided with diagnostic suggestions from AI engine to ensure secure diagnoses, recommendations and treatments. Also, we are working for de-centralized health care service, currently in the process of providing several services to developing countries such as Uganda.
               \item As a part of the AI team in Byon8, I have been responsible for data preprocessing, data mining, and building a predictive model using a wide variety of machine learning models. I had an opportunity to stepped into the industry where I can have hands-on experience in implementing production machine learning systems, and also a solid understanding of ML theory. During the internship, I wrote my Master's thesis about building a tree-based model that can help diagnose diabetes.
               \end{itemize}}
            {Python, R, MongoDB}
  \emptySeparator
  
  
   \experience
    {September 2017} {Digital Ambassador | Svenska Institutet}{Stockholm}{Sweden}
    {Jun 2019}    {\begin{itemize}
               \item Studyinsweden is an organization built and maintained by the Swedish Institute(Svenska Institutet) to the public agency tasked with promoting Sweden for prospective international students abroad. We provide contents regarding the Swedish higher education system, finding and applying for a programme, searching for scholarships, living as an international student in Sweden and learning Swedish.
               \item I was part of blog and Instagram team as a digital ambassador, responsible for writing blog posts for the Study in Sweden blog. Also had a responsibility of managing official Instagram account \href{https://www.instagram.com/studyinsweden/}{@Studyinsweden} for posting photos, uploading stories and taking part in Live broadcasts. Also, work with responding to user comments and answer e-mail questions from prospective students.
               \end{itemize}}
            {Marketing}
  \emptySeparator
  
  
 \experience
    {September 2017} {Data Analyst Intern | ZipFund}{Seoul}{Korea}
    {January 2017}    {\begin{itemize}
               \item ZipFund is a BigData and AI Tech startup in real estate. It provides advisory service to financial institutes, apartment automated valuation modeling service allowing banks and lenders use ZipFund's data solution for their mortgage lending process automation.

               \item  My main task was to find meaningful insights that would help people estimate house price. I used SQL to retrieve data and analyzed with R. I tested various topics with statistical models. Two main ways to visualize housing prices differ depending on the floor within the apartment. Also to find a similar price pattern between districts by applying dimension reduction, and to clustering houses sharing similar price variations. 
               \end{itemize}}
            {Marketing}
  \emptySeparator
  
  
  
  
\end{experiences}
