% Awesome Source CV LaTeX Template
%
% This template has been downloaded from:
% https://github.com/darwiin/awesome-neue-latex-cv
%
% Author:
% Christophe Roger
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)

%Section: Project
\sectionTitle{Projects}{\faLaptop}


\begin{projects}
\project{Predicting Diabetes Using Tree-based Methods }{2019}{Uppsala University, Department of Statistics, Independent thesis Advanced level (degree of Master (Two Years)}
{ \website{http://uu.diva-portal.org/smash/get/diva2:1323917/FULLTEXT01.pdf}{Download}\github{hyunjin-nam/thesis-diabetes}\\ The aim of this study is to develop a statistical model to predict type 2 diabetes based on the tree-based model. Furthermore, the aim to compare classification with current medical criteria. Decision Tree, Random Forest, Boosting with a XGBoost algorithm is used as a classification method to predict diabetes. The results show XGBoost outperformed the two other models in yielding highest classification rate, with a 84.6 percent test accuracy. Two interesting findings from this paper are: 1) Ensemble methods such as Random forest and boosting can be easily overfitted on training data, but this problem can be solved with correct hyper-parameter tunning. And 2) Tree-based methods such as XGboost and Random Forest can solve variables' multicollinearity problems.}
{Machine learning, Medical health, R, Python}

\end{projects}


\begin{projects}
\project{Music Classification Project}{2019}
{ \github{hyunjin-nam/course-MachineLearning} }
{This project aims to learn statistical machine learning from Uppsala university as a part of course work. The task is to classify a set of 100 songs and predict whether a specific person would like them or not, with the help from a training data set with 500 songs. Random Forest, Boosting, Logistic Regression was applied to the analysis.}
{R, Machine learning}

\end{projects}

\begin{projects}
\project{Hyunjinnam.com}{2018 - Present}
{\website{https://hyunjinnam.com}{Check here!} \github{hyunjin-nam/homepage-vuepress} }
{I love learning a new programming language and creating my content. 
This is the life-time project that I would like to keep as a hobby. I like to create contents I enjoy creating contents and communicating with people, no matter through conversation, text, photography or code. I wanted to have my webpage where I can post materials and share with others. First, I build the page from scratch using HTML5, CSS and jQuery. And recently renovated using Vuepress and markdown,  get to know more about the joy of coding by exploring other's intention in their code and try to adjust it with my purpose of use. Please come and visit my webpage and find more about me!}
{Vuepress, HTML, CSS, JQuery}   
\end{projects}

